Male-biased sexual selection, but not sexual dichromatism, predicts speciation

### 2019-05-22 Sexual Selection and Speciation.Rmd
Updated DR and ND: Now with 1000 models

```{r, message=FALSE, warning=FALSE}
library(ggplot2)
library(pander)
library(knitr)
library(tidyr)
library(mgcv)
library(diversitree)
library(repmis)
library(lme4)
library(ape)
library(geiger)
library(grid)
library(gridExtra)
library(nlme)
library(phytools)
library(brms)
library(ggridges)
library(caper)
library(purrr)
library(reshape2)
library(ggExtra)
library(grid)
library(dplyr)
library(BAMMtools)
library(gridExtra)
library(car)
library(coda)
library(MuMIn)
library(parallel)
library(HDInterval)
library(phangorn)
library(kableExtra)
library(RColorBrewer)
library(tibble)
library(stargazer)
library(ggraph)
#devtools::install_github("Ax3man/phylopath")
library(phylopath)
library("EBImage") # for images
library("ggtree")
source("bamm_extinction/functions/check_and_fix_ultrametric.R")
source("functions/essim.R")
source("functions/diversification_rate_calculation.R")
source("functions/Vdodge_function.R")
source('functions/symmetrise_scale.R')
source('functions/Correlation_matrix.R')
source('functions/gheatmap2.R') #Gets rid of spaces between tiles
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(cache=TRUE)
```

@@

#Take the restricted data and make it simpler with just responses and predictors.Note that we join the es.values for the 100 trees
DR.model.data <- lapply(es.list, function(x) { #es.list is a list of ES values calculated earlier
  left_join(restricted.data %>% dplyr::select(binomial, TipLabel, SDi, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP), 
            x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ES")), 
            by = "TipLabel")
})

#PGLS needs tiplabel as rowname
DR.model.data <- lapply(DR.model.data, function(x) {
  tibble::column_to_rownames(x, "TipLabel")})

#Use mapply to create a list of PGLS global models
DR.pgls.models <- mcmapply(function(x,y) {
  gls(ES ~ SDi 
         + log(range.size.m2)
         + bioclim4 #Seasonal variation
         + residuals.PC1 #Spatial variation
         + PC1.LIG #Long-term climate variation
         + NPP,
    corPagel(0.985, phy = y, fixed = TRUE), 
    data = x, 
    method = "REML")
}, x = DR.model.data, y = pruned.trees,
SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
mc.cores = 8) #Specify core number

saveRDS(DR.pgls.models, "data/DR.pgls.models.rds")

#Now for Node Density:
ND.model.data <- lapply(nd.list, function(x) {
  left_join(restricted.data %>% dplyr::select(binomial, TipLabel, SDi, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP), 
            x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ND")), 
            by = "TipLabel")
})

#PGLS needs tiplabel as rowname
ND.model.data <- lapply(ND.model.data, function(x) {
  tibble::column_to_rownames(x, "TipLabel")})

#Use mapply to create a list of PGLS global models
ND.pgls.models <- mcmapply(function(x,y) {
gls(ND ~ SDi 
         + log(range.size.m2)
         + bioclim4 #Seasonal variation
         + residuals.PC1 #Spatial variation
         + PC1.LIG #Long-term climate variation
         + NPP,
    corPagel(0.9996, phy = y, fixed = TRUE), 
    data = x, 
    method = "REML")
}, x = ND.model.data, y = pruned.trees, 
SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
mc.cores = 8) #Specify core number

saveRDS(ND.pgls.models, "data/ND.pgls.models.rds")
```

From these models we obtained a distribution of the estimates for the models alongside the 95 % CIs of the MCC model. This enabled us to show the variation between trees, and the variation associated with the top MCC model.

```{r, fig.height = 8, fig.width = 4, message = FALSE, warning = FALSE}
DR.pgls.models <- readRDS("data/DR.pgls.models.rds")
MCC.DR.top <- readRDS('data/MCC.DR.top.rds')

DR.pgls.summary <- lapply(DR.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

MCC.DR.summary <- data.frame(MCC.DR.top$coefficients, confint(MCC.DR.top)) %>% tibble::rownames_to_column()

DR.pgls.summary <- bind_rows(DR.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

colnames(MCC.DR.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

DR.plot <-DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  geom_jitter(shape = 21, alpha = 0.5, size = 0.75)+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

@@

ND.pgls.models <- readRDS("data/ND.pgls.models.rds")
MCC.ND.top <- readRDS('data/MCC.ND.top.rds')

ND.pgls.summary <- lapply(ND.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

MCC.ND.summary <- data.frame(MCC.ND.top$coefficients, confint(MCC.ND.top)) %>% tibble::rownames_to_column()

ND.pgls.summary <- bind_rows(ND.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

colnames(MCC.ND.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

```{r, warning=F, error = F, fig.height = 8, fig.width = 4}
BAMM.lambda.pgls.models <- readRDS("data/BAMM.lambda.pgls.models.rds")
MCC.Lambda.top <- readRDS('data/MCC.Lambda.top.rds')

@@

@@

MCC.lambda.summary <- data.frame(MCC.Lambda.top$coefficients, confint(MCC.Lambda.top)) %>% tibble::rownames_to_column()

@@

colnames(MCC.lambda.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

BAMM.mu.pgls.models <- readRDS("data/BAMM.mu.pgls.models.rds")
MCC.Mu.top <- readRDS('data/MCC.Mu.top.rds')

@@

MCC.mu.summary <- data.frame(MCC.Mu.top$coefficients, confint(MCC.Mu.top)) %>% tibble::rownames_to_column()

@@

colnames(MCC.mu.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

**Table S7:** The estimates of the MCC models plotted above are based on the following data tables.
```{r}
MCC.DR.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates")
MCC.ND.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates")
MCC.lambda.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates")
MCC.mu.summary %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates")
```

@@

#Run the 100 models for DR and ND using the best model:
Subset.data.noMCC <- SS.subset %>% dplyr::select(TipLabel, Sexual_selection_ppca, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP)

#Take the restricted data and make it simpler with just responses and predictors.Note that we join the es.values for the 100 trees
Subset.DR.model.data <- lapply(es.list, function(x) { #es.list is a list of ES values calculated earlier
  left_join(Subset.data.noMCC, 
            x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "DR")), 
            by = "TipLabel")
})

#PGLS needs tiplabel as rowname
Subset.DR.model.data <- lapply(Subset.DR.model.data, function(x) {
  tibble::column_to_rownames(x, "TipLabel")})

#Prune the trees
Subset.pruned.trees<-lapply(passerine.trees, function(x) {
  drop.tip(x,x$tip.label[-match(SS.subset$TipLabel, x$tip.label)])
})

#Use mapply to create a list of PGLS global models
Subset.DR.pgls.models <- mcmapply(function(x,y) {
  gls(DR ~ Sexual_selection_ppca 
         + log(range.size.m2)
         + bioclim4 #Seasonal variation
         + residuals.PC1 #Spatial variation
         + PC1.LIG #Long-term climate variation
         + NPP,
    correlation = corPagel(0.9711, phy = y, fixed = TRUE), 
    data = x, 
    method = "REML")
}, x = Subset.DR.model.data, y = Subset.pruned.trees,
SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
mc.cores = 8) #Specify core number

saveRDS(Subset.DR.pgls.models, "data/Subset.DR.pgls.models.rds")

#Now for Node Density:
Subset.ND.model.data <- lapply(nd.list, function(x) { #es.list is a list of ES values calculated earlier
  left_join(Subset.data.noMCC, 
            x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ND")), 
            by = "TipLabel")
})

#PGLS needs tiplabel as rowname
Subset.ND.model.data <- lapply(Subset.ND.model.data, function(x) {
  tibble::column_to_rownames(x, "TipLabel")})

#Use mapply to create a list of PGLS global models
Subset.ND.pgls.models <- mcmapply(function(x,y) {
gls(ND ~ Sexual_selection_ppca 
         + log(range.size.m2)
         + bioclim4 #Seasonal variation
         + residuals.PC1 #Spatial variation
         + PC1.LIG #Long-term climate variation
         + NPP,
    corPagel(1, phy = y, fixed = TRUE), 
    data = x, 
    method = "REML")
}, x = Subset.ND.model.data, y = Subset.pruned.trees, 
SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
mc.cores = 8) #Specify core number

saveRDS(Subset.ND.pgls.models, "data/Subset.ND.pgls.models.rds")

@@

```{r}
Subset.DR.pgls.models <- readRDS("data/Subset.DR.pgls.models.rds")
Subset.MCC.DR.top <- readRDS('data/Subset.MCC.DR.top.rds')

Subset.cols <- brewer.pal(n = 7, name = "Dark2")[-6]

Subset.DR.pgls.summary <- lapply(Subset.DR.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

Subset.MCC.DR.summary <- data.frame(Subset.MCC.DR.top$coefficients, confint(Subset.MCC.DR.top)) %>% tibble::rownames_to_column()

Subset.DR.pgls.summary <- bind_rows(Subset.DR.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

colnames(Subset.MCC.DR.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

Subset.ND.pgls.models <- readRDS("data/Subset.ND.pgls.models.rds")
Subset.MCC.ND.top <- readRDS('data/Subset.MCC.ND.top.rds')

Subset.ND.pgls.summary <- lapply(Subset.ND.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

Subset.MCC.ND.summary <- data.frame(Subset.MCC.ND.top$coefficients, confint(Subset.MCC.ND.top)) %>% tibble::rownames_to_column()

Subset.ND.pgls.summary <- bind_rows(Subset.ND.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

colnames(Subset.MCC.ND.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

Subset.MCC.Lambda.summary <- data.frame(Subset.MCC.Lambda.top$coefficients, confint(Subset.MCC.Lambda.top)) %>% tibble::rownames_to_column()

@@

colnames(Subset.MCC.Lambda.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

@@

Subset.Mu.pgls.summary <- lapply(Subset.BAMM.Mu.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})

Subset.MCC.Mu.summary <- data.frame(Subset.MCC.Mu.top$coefficients, confint(Subset.MCC.Mu.top)) %>% tibble::rownames_to_column()

Subset.Mu.pgls.summary <- bind_rows(Subset.Mu.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

colnames(Subset.MCC.Mu.summary) <- c("Parameter", "Estimate", "LCI", "UCI")

>>>>

```{r setup, message=FALSE, warning=FALSE}
library(ggplot2)
library(pander)
library(knitr)
library(tidyr)
library(mgcv)
library(diversitree)
library(repmis)
library(lme4)
library(ape)
library(geiger)
library(grid)
library(gridExtra)
library(nlme)
library(phytools)
library(brms)
library(ggridges)
library(caper)
library(purrr)
library(reshape2)
library(ggExtra)
library(grid)
library(dplyr)
library(BAMMtools)
library(gridExtra)
library(car)
library(coda)
library(MuMIn)
library(parallel)
library(HDInterval)
library(phangorn)
library(kableExtra)
library(RColorBrewer)
library(tibble)
library(stargazer)
library(ggraph)
library(stringr)
#devtools::install_github("Ax3man/phylopath")
library(phylopath)
library("EBImage") # for images
library("ggtree")
source("bamm_extinction/functions/check_and_fix_ultrametric.R")
source("functions/essim.R")
source("functions/diversification_rate_calculation.R")
source("functions/Vdodge_function.R")
source('functions/symmetrise_scale.R')
source('functions/Correlation_matrix.R')
source('functions/gheatmap2.R') #Gets rid of spaces between tiles
knitr::opts_chunk$set(cache=TRUE)
```

@@

# No longer used now that we use 1000 trees

# #Take the restricted data and make it simpler with just responses and predictors.Note that we join the es.values for the 100 trees
# DR.model.data <- lapply(es.list, function(x) { #es.list is a list of ES values calculated earlier
#   left_join(restricted.data %>% dplyr::select(binomial, TipLabel, SDi, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP), 
#             x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ES")), 
#             by = "TipLabel")
# })
# 
# #PGLS needs tiplabel as rowname
# DR.model.data <- lapply(DR.model.data, function(x) {
#   tibble::column_to_rownames(x, "TipLabel")})
# 
# #Prune the trees
# pruned.trees<-lapply(passerine.trees, function(x) {
#   drop.tip(x,x$tip.label[-match(restricted.data$TipLabel, x$tip.label)])
# })
# 
# #Use mapply to create a list of PGLS global models
# DR.pgls.models <- mcmapply(function(x,y) {
#   gls(ES ~ SDi 
#          + log(range.size.m2)
#          + bioclim4 #Seasonal variation
#          + residuals.PC1 #Spatial variation
#          + PC1.LIG #Long-term climate variation
#          + NPP,
#     corPagel(0.985, phy = y, fixed = TRUE), 
#     data = x, 
#     method = "REML")
# }, x = DR.model.data, y = pruned.trees,
# SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
# mc.cores = 8) #Specify core number 
# 
# saveRDS(DR.pgls.models, "data/DR.pgls.models.rds")
# 
# #Now for Node Density:
# ND.model.data <- lapply(nd.list, function(x) {
#   left_join(restricted.data %>% dplyr::select(binomial, TipLabel, SDi, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP), 
#             x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ND")), 
#             by = "TipLabel")
# })
# 
# #PGLS needs tiplabel as rowname
# ND.model.data <- lapply(ND.model.data, function(x) {
#   tibble::column_to_rownames(x, "TipLabel")})
# 
# #Use mapply to create a list of PGLS global models
# ND.pgls.models <- mcmapply(function(x,y) {
# gls(ND ~ SDi 
#          + log(range.size.m2)
#          + bioclim4 #Seasonal variation
#          + residuals.PC1 #Spatial variation
#          + PC1.LIG #Long-term climate variation
#          + NPP,
#     corPagel(0.9996, phy = y, fixed = TRUE), 
#     data = x, 
#     method = "REML")
# }, x = ND.model.data, y = pruned.trees, 
# SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
# mc.cores = 8) #Specify core number 
# 
# saveRDS(ND.pgls.models, "data/ND.pgls.models.rds")
```

From these models we obtained a distribution of the estimates for the models alongside the 95 % CIs of the MCC model. This enabled us to show the variation between trees, and the variation associated with the top MCC model. Given the variability across trees we ran 1000 ND and DR models, each allowed to estimate a phylogenetic signal ($\lambda$). The models were saved as an `.rds` object and read back into R with key coefficients extracted. Below we provide the code for this:

```{r, eval = F}
##########################################################
####### Read in DR models and extract estimates: #########
##########################################################

#We ran DR and ND models on 1000 trees
files.DR.SD <- list.files(path = "/Users/justincally/Dropbox/Runs Spartan/DR_SD/", pattern = "\\.rds$", full.names = TRUE) #1000 models
df <- list()
lapply(files.DR.SD, function(x) {
  tryCatch({
  model.x <- readRDS(x)
  name.x <- str_sub(x, -19, -5)
  df[[name.x]] <<- data.frame(model.x$coefficients,
                              confint(model.x),
                              coef(summary(model.x))[,2], #Std.Error
                              coef(summary(model.x))[,3], #t-val
                              coef(summary(model.x))[,4], #pval
                              model.x[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = name.x) %>% tibble::rownames_to_column()
  rm(model.x)
  gc(verbose = FALSE)
  },
  error = function(e) NULL
  )
})
DR.pgls.summary <- bind_rows(df) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))
#saveRDS(DR.pgls.summary, "data/DR.pgls.summary.rds") #Save a simple df with the model and coeff

##########################################################
####### Read in ND models and extract estimates: #########
##########################################################

files.ND.SD <- list.files(path = "/Users/justincally/Dropbox/Runs Spartan/ND_SD/", pattern = "\\.rds$", full.names = TRUE) #1000 models
df <- list()
lapply(files.ND.SD, function(x) {
  tryCatch({
  model.x <- readRDS(x) 
  name.x <- str_sub(x, -19, -5)
  df[[name.x]] <<- data.frame(model.x$coefficients, 
                              confint(model.x), 
                              coef(summary(model.x))[,2], #Std.Error
                              coef(summary(model.x))[,3], #t-val
                              coef(summary(model.x))[,4], #pval
                              model.x[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = name.x) %>% tibble::rownames_to_column()
  rm(model.x)
  gc(verbose = FALSE)
  },
  error = function(e) NULL
  )
})
ND.pgls.summary <- bind_rows(df) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))
#saveRDS(ND.pgls.summary, "data/ND.pgls.summary.rds") #Save a simple df with the model and coeff
```

```{r, fig.height = 8, fig.width = 4, message = FALSE, warning = FALSE}
#Read in the 1000 tree summary df and the MCC tree model
DR.pgls.summary <- readRDS("data/DR.pgls.summary.rds")
MCC.DR.top <- readRDS('data/MCC.DR.top.rds')
MCC.DR.summary <-  data.frame(MCC.DR.top$coefficients,
                              confint(MCC.DR.top),
                              coef(summary(MCC.DR.top))[,2], #Std.Error
                              coef(summary(MCC.DR.top))[,3], #t-val
                              coef(summary(MCC.DR.top))[,4], #pval
                              MCC.DR.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

ND.pgls.summary <- readRDS("data/ND.pgls.summary.rds")
MCC.ND.top <- readRDS('data/MCC.ND.top.rds')
MCC.ND.summary <- data.frame(MCC.ND.top$coefficients,
                              confint(MCC.ND.top),
                              coef(summary(MCC.ND.top))[,2], #Std.Error
                              coef(summary(MCC.ND.top))[,3], #t-val
                              coef(summary(MCC.ND.top))[,4], #pval
                              MCC.ND.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

@@

DR.plot <-DR.pgls.summary %>% filter(Parameter != "(Intercept)") %>% 
  ggplot(aes(x = Estimate, y = Parameter, fill = Parameter)) +
  geom_density(aes(y = ..scaled..),
               position = position_nudge(y= 0.6))+
  #geom_errorbarh(aes(xmin = LCI, xmax = UCI, colour = Parameter), position = position_jitter(seed = 1), height = 0)+
  geom_point(shape = 21, alpha = 0.5, size = 0.75, position = position_jitter(seed = 1))+
  geom_vline(xintercept = 0)+
  theme_minimal()+
  theme(axis.text.y = element_blank(),
        legend.position = "none")

@@

@@

```{r, warning=F, error = F, fig.height = 8, fig.width = 4}
BAMM.lambda.pgls.models <- readRDS("data/BAMM.lambda.pgls.models.rds")

@@

#Now plot this for Lambda

MCC.Lambda.top <- readRDS('data/MCC.Lambda.top.rds')
MCC.lambda.summary <- data.frame(MCC.Lambda.top$coefficients,
                              confint(MCC.Lambda.top),
                              coef(summary(MCC.Lambda.top))[,2], #Std.Error
                              coef(summary(MCC.Lambda.top))[,3], #t-val
                              coef(summary(MCC.Lambda.top))[,4], #pval
                              MCC.Lambda.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

@@

@@

@@

BAMM.mu.pgls.models <- readRDS("data/BAMM.mu.pgls.models.rds")

@@

@@

#Now plot this for Lambda

MCC.Mu.top <- readRDS('data/MCC.Mu.top.rds')
MCC.mu.summary <- data.frame(MCC.Mu.top$coefficients,
                              confint(MCC.Mu.top),
                              coef(summary(MCC.Mu.top))[,2], #Std.Error
                              coef(summary(MCC.Mu.top))[,3], #t-val
                              coef(summary(MCC.Mu.top))[,4], #pval
                              MCC.Mu.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% 
  tibble::rownames_to_column() %>% 
  `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))

@@

**Table S7:** The estimates of the MCC models plotted above are based on the following data tables.
```{r}
MCC.DR.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC DR Estimates", split.table = Inf)
MCC.ND.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC ND Estimates", split.table = Inf)
MCC.lambda.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Speciation Estimates", split.table = Inf)
MCC.mu.summary %>% select(-model_name) %>% filter(Parameter != "(Intercept)") %>% pander(caption = "MCC BAMM Extinction Estimates", split.table = Inf)
```

@@

## No longer needed

# #Run the 100 models for DR and ND using the best model:
# Subset.data.noMCC <- SS.subset %>% dplyr::select(TipLabel, Sexual_selection_ppca, range.size.m2, bioclim4, residuals.PC1, PC1.LIG, NPP)
# 
# #Take the restricted data and make it simpler with just responses and predictors.Note that we join the es.values for the 100 trees
# Subset.DR.model.data <- lapply(es.list, function(x) { #es.list is a list of ES values calculated earlier
#   left_join(Subset.data.noMCC, 
#             x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "DR")), 
#             by = "TipLabel")
# })
# 
# #PGLS needs tiplabel as rowname
# Subset.DR.model.data <- lapply(Subset.DR.model.data, function(x) {
#   tibble::column_to_rownames(x, "TipLabel")})
# 
# #Prune the trees
# Subset.pruned.trees<-lapply(passerine.trees, function(x) {
#   drop.tip(x,x$tip.label[-match(SS.subset$TipLabel, x$tip.label)])
# })
# 
# #Use mapply to create a list of PGLS global models
# Subset.DR.pgls.models <- mcmapply(function(x,y) {
#   gls(DR ~ Sexual_selection_ppca 
#          + log(range.size.m2)
#          + bioclim4 #Seasonal variation
#          + residuals.PC1 #Spatial variation
#          + PC1.LIG #Long-term climate variation
#          + NPP,
#     correlation = corPagel(0.9711, phy = y, fixed = TRUE), 
#     data = x, 
#     method = "REML")
# }, x = Subset.DR.model.data, y = Subset.pruned.trees,
# SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
# mc.cores = 8) #Specify core number 
# 
# saveRDS(Subset.DR.pgls.models, "data/Subset.DR.pgls.models.rds")
# 
# #Now for Node Density:
# Subset.ND.model.data <- lapply(nd.list, function(x) { #es.list is a list of ES values calculated earlier
#   left_join(Subset.data.noMCC, 
#             x %>% as.data.frame() %>% tibble::rownames_to_column() %>% `colnames<-`(c("TipLabel", "ND")), 
#             by = "TipLabel")
# })
# 
# #PGLS needs tiplabel as rowname
# Subset.ND.model.data <- lapply(Subset.ND.model.data, function(x) {
#   tibble::column_to_rownames(x, "TipLabel")})
# 
# #Use mapply to create a list of PGLS global models
# Subset.ND.pgls.models <- mcmapply(function(x,y) {
# gls(ND ~ Sexual_selection_ppca 
#          + log(range.size.m2)
#          + bioclim4 #Seasonal variation
#          + residuals.PC1 #Spatial variation
#          + PC1.LIG #Long-term climate variation
#          + NPP,
#     corPagel(1, phy = y, fixed = TRUE), 
#     data = x, 
#     method = "REML")
# }, x = Subset.ND.model.data, y = Subset.pruned.trees, 
# SIMPLIFY = FALSE, #Prevents the catastrophic loss of structure, names and attributes
# mc.cores = 8) #Specify core number 
# 
# saveRDS(Subset.ND.pgls.models, "data/Subset.ND.pgls.models.rds")

@@

```{r, eval = F}

##########################################################
####### Read in DR models and extract estimates: #########
##########################################################

#We ran DR and ND models on 1000 trees
files.DR.SS <- list.files(path = "/Users/justincally/Dropbox/Runs Spartan/DR_SS/", pattern = "\\.rds$", full.names = TRUE) #1000 models
df <- list()
rds.list <- list()
models <- list()
c.list <- NULL

lapply(files.DR.SS, function(x) {
models <- readRDS(x)
rds.list <- unlist(models, recursive = F, use.names = T)
c.list <<- c(c.list, rds.list[-grep(".log", names(rds.list))])
rm(models)
rm(rds.list)
gc()
})

lapply(names(c.list), function(x) {
  tryCatch({
  model <- c.list[[x]]
  df[[x]] <<- data.frame(model$coefficients,
                              confint(model),
                              coef(summary(model))[,2], #Std.Error
                              coef(summary(model))[,3], #t-val
                              coef(summary(model))[,4], #pval
                              model[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = x) %>% tibble::rownames_to_column()
  gc(verbose = FALSE)
  },
  error = function(e) NULL
  )
})

Subset.DR.pgls.summary <- bind_rows(df) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))
#saveRDS(Subset.DR.pgls.summary, "data/Subset.DR.pgls.summary.rds") #Save a simple df with the model and coeff

#read in 1000 trees:

#We ran DR and ND models on 1000 trees
files.ND.SS <- list.files(path = "/Users/justincally/Dropbox/Runs Spartan/ND_SS/", pattern = "\\.rds$", full.names = TRUE) #1000 models
df <- list()
rds.list <- list()
models <- list()
c.list <- NULL

lapply(files.ND.SS, function(x) {
models <- readRDS(x)
rds.list <- unlist(models, recursive = F, use.names = T)
c.list <<- c(c.list, rds.list[-grep(".log", names(rds.list))])
rm(models)
rm(rds.list)
gc()
})

lapply(names(c.list), function(x) {
  tryCatch({
  model <- c.list[[x]]
  df[[x]] <<- data.frame(model$coefficients,
                              confint(model),
                              coef(summary(model))[,2], #Std.Error
                              coef(summary(model))[,3], #t-val
                              coef(summary(model))[,4], #pval
                              model[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = x) %>% tibble::rownames_to_column()
  gc(verbose = FALSE)
  },
  error = function(e) NULL
  )
})

Subset.ND.pgls.summary <- bind_rows(df) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name"))
#saveRDS(Subset.ND.pgls.summary, "data/Subset.ND.pgls.summary.rds") #Save a simple df with the model and coeff
rm(c.list)
############################
```

```{r}
Subset.DR.pgls.summary <- readRDS("data/Subset.DR.pgls.summary.rds")
Subset.ND.pgls.summary <- readRDS("data/Subset.ND.pgls.summary.rds")

#Cols for plot: 
Subset.cols <- brewer.pal(n = 7, name = "Dark2")[-6]

### MCC
Subset.MCC.DR.top <- readRDS('data/Subset.MCC.DR.top.rds')

Subset.MCC.DR.summary <- data.frame(Subset.MCC.DR.top$coefficients,
                              confint(Subset.MCC.DR.top),
                              coef(summary(Subset.MCC.DR.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.DR.top))[,3], #t-val
                              coef(summary(Subset.MCC.DR.top))[,4], #pval
                              Subset.MCC.DR.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.DR.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

@@

Subset.MCC.ND.top <- readRDS('data/Subset.MCC.ND.top.rds')

Subset.MCC.ND.summary <- data.frame(Subset.MCC.ND.top$coefficients,
                              confint(Subset.MCC.ND.top),
                              coef(summary(Subset.MCC.ND.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.ND.top))[,3], #t-val
                              coef(summary(Subset.MCC.ND.top))[,4], #pval
                              Subset.MCC.ND.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.ND.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

@@

@@

#MCC

Subset.MCC.Lambda.summary <- data.frame(Subset.MCC.Lambda.top$coefficients,
                              confint(Subset.MCC.Lambda.top),
                              coef(summary(Subset.MCC.Lambda.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.Lambda.top))[,3], #t-val
                              coef(summary(Subset.MCC.Lambda.top))[,4], #pval
                              Subset.MCC.Lambda.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.Lambda.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")

@@

Subset.Mu.pgls.summary <- lapply(Subset.BAMM.Mu.pgls.models, function(x) {
  data.frame(x$coefficients, confint(x)) %>% tibble::rownames_to_column()
})
Subset.Mu.pgls.summary <- bind_rows(Subset.Mu.pgls.summary) %>% `colnames<-`(c("Parameter", "Estimate", "LCI", "UCI"))

#MCC

Subset.MCC.Mu.summary <- data.frame(Subset.MCC.Mu.top$coefficients,
                              confint(Subset.MCC.Mu.top),
                              coef(summary(Subset.MCC.Mu.top))[,2], #Std.Error
                              coef(summary(Subset.MCC.Mu.top))[,3], #t-val
                              coef(summary(Subset.MCC.Mu.top))[,4], #pval
                              Subset.MCC.Mu.top[["modelStruct"]][["corStruct"]][1], #lambda value
                              model = "MCC_model") %>% tibble::rownames_to_column()

colnames(Subset.MCC.Mu.summary) <- c("Parameter", "Estimate", "LCI", "UCI", "SE", "tval", "pval" , "lambda" ,"model_name")
